Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-03-16 doc/paper.Rmd
couple of edits

Markings made by screw driver tips \citep{chumbley} are longer and pronounced and about 7 mm in length \citep{manytoolmarks1}, while the groove to groove length of the bullet lands from the Hamby study \citep{hamby} are about 2mm in length. The Ruger pistol barrels used in the  Hamby study have a 9mm caliber. This means that bullets used in these pistols have land markings of only about a quarter of the size of screwdriver toolmarks used by \citet{chumbley, hadler}, therefore raising a problem of distinctiveness. One way to investigate this is to evaluate bullet striations at different resolutions. This gives us an incentive to use both the NIST and Iowa State scans and investigate the effect of length of the digitized mark on the working of the algorithm. Apart from this, the algorithm developed by \citet{hadler} has only been tested for flatter and wider surfaces which have negligible curvature, whereas striations on bullets are made on their curved surfaces. Therefore, using methods proposed for toolmarks need adaptation in order to give tangible results for bullets. Another challenge that arises from these topographical differences, is the understanding of that effect of different levels of smoothing. Especially investigating its effect on the algorithm performance when signatures are being compared and when raw markings or profiles are being compared.

@@

Thus, the comaparison windows have a direct influence on the false positives and false negatives, making identification of the optimum sizes of these windows very important. This raises important questions about how and what parameter settings need to be chosen for bullet land comparison. Something similar is done in \citet{afte-chumbley} for toolmark comparisons of slip-joint pliers where optimum window sizes are determined. There is a need to figure out the best parameter settings which minimizes the errors for unsmoothed markings or profiles and pre-processed signatures. An analysis of these error rates and comparison with other methods will help us understand the adaptibility of the chumbley score to bullets.

>>>>

Markings made by screw driver tips \citep{chumbley} are longer and pronounced and about 7 mm in length \citep{manytoolmarks1}, while the groove to groove length of the bullet lands from the Hamby study \citep{hamby} are about 2mm in length. The Ruger pistol barrels used in the  Hamby study have a 9mm caliber. This means that bullets used in these pistols have land markings of only about a quarter of the size of screwdriver toolmarks used by \citet{chumbley, hadler}, therefore raising the problem of potential loss in power of the test. 
\hh{The Chumbley score allows a separation of a toolmark into raw and normalized digitized versions. Originally, this mechanism is intended to separate between class characteristics and individual markings, however, in the setting of matching bullet striae, we could also use it to separate bullet curvature in profiles from signatures before matching signatures. }

<!--One way to investigate this is to evaluate bullet striations at different resolutions. This gives us an incentive to use both the NIST and Iowa State scans and investigate the effect of length of the digitized mark on the working of the algorithm. Apart from this, the algorithm developed by \citet{hadler} has only been tested for flatter and wider surfaces which have negligible curvature, whereas striations on bullets are made on their curved surfaces. Therefore, using methods proposed for toolmarks need adaptation in order to give tangible results for bullets. Another challenge that arises from these topographical differences, is the understanding of that effect of different levels of smoothing. Especially investigating its effect on the algorithm performance when signatures are being compared and when raw markings or profiles are being compared.

@@

Thus, the comaparison windows have a direct influence on the false positives and false negatives, making identification of the optimum sizes of these windows very important. This raises important questions about how and what parameter settings need to be chosen for bullet land comparison. Something similar is done in \citet{afte-chumbley} for toolmark comparisons of slip-joint pliers where optimum window sizes are determined. There is a need to figure out the best parameter settings which minimizes the errors for unsmoothed markings or profiles and pre-processed signatures. An analysis of these error rates and comparison with other methods will help us understand the adaptibility of the chumbley score to bullets.  
-->
